A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-21 4_method.tex
redo center marking section

\begin{figure}
\centering
%\begin{subfigure}{0.45\textwidth}
%\includegraphics[width=\columnwidth]{sources/method/parabola_dip.pdf}
%\caption{asf}
%\end{subfigure}
%\begin{subfigure}{0.45\textwidth}
\includegraphics[width=\columnwidth]{sources/method/point-point_and_point-line_segments.pdf}
%\caption{Transitioning}
%\end{subfigure}
\caption{
Skeletal trapezoidation domain decomposition.
Medial axis (red and blue) is augmented with (gray) edges connecting each node to its nearest support points in the outline shape.
Parabolic medial axis segments are discretized and likewise for segments generated by two concave outline vertices, because the feature radius (black text in microns) doesn't increase linearly along those segments.
The blue segments are significant according to $\alpha_\text{max} = 135\degree$.
}
\label{discretization}
\end{figure}

\subsection{Center classification}\label{sec_center_classification}
\todo{TODO: explain section title!}

We assign a bead count to each node in the skeleton which is in `the center' of the shape in a sense which will be defined in \cref{sec:significance_measure}.
Around regions where the bead count changes we introduce transition regions, so that we can smoothly change between regions with different bead count.

We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
We also mark whole bones as being central if they are significant according to a common significance measure.

\subsubsection{Significance measure}\label{sec:significance_measure}
Places where the naive concentric toolpathing strategy would create large underfill and overfill areas are locations which are in some sense \emph{central} to the shape.
This can be formalized by looking at the significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

@@

\begin{figure}
\centering
\includegraphics[width=\columnwidth]{sources/method/naive_overfill_underfill.pdf}
\caption{
Overfill and underfill areas in a naive beading using a constant bead width $w$ of a wedge area with vertex angle $\beta$.
The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
}
\label{naive_overfill_underfill}
\end{figure}

A computationally efficient way to compute $\alpha$ can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
See \cref{distance_based_angles}.
This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of significant regions.
See \cref{discretization}.

@@

\subsubsection{Marking filtering}
Using the significance measure and the local maximum feature radius condition we initialize all marked bones and nodes.
We then filter out high frequency changes in the marking in order to ensure smooth output toolpaths. 
We perform filtering on the unmarked regions, so that the properties of significant regions mentioned above remain valid.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges (which cannot branch because of \cref{single_upward_edge}).
If the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.

>>>>

\begin{figure}
\centering
%\begin{subfigure}{0.45\textwidth}
%\includegraphics[width=\columnwidth]{sources/method/parabola_dip.pdf}
%\caption{asf}
%\end{subfigure}
%\begin{subfigure}{0.45\textwidth}
\includegraphics[width=.5\columnwidth]{sources/method/point-point_and_point-line_segments.pdf}
%\caption{Transitioning}
%\end{subfigure}
\caption{
Skeletal trapezoidation domain decomposition.
Medial axis (red and blue) is augmented with (gray) edges connecting each node to its nearest support points in the outline shape.
Parabolic medial axis segments are discretized and likewise for segments generated by two concave outline vertices, because the feature radius (black text in microns) doesn't increase linearly along those segments.
The blue segments are significant according to $\alpha_\text{max} = 135\degree$.
}
\label{discretization}
\end{figure}

\subsection{Center classification}\label{sec_center_classification}
The naive method of performing constant width offset produces large overfill and underfill areas on central regions of the skeleton.
These central regions present themselves as upper ridges in the mountains of the UoC surface.
This sections covers what parts of the UoC will be marked as being central, rather than peripheral.

We mark a node of the skeleton as central if its feature radius is larger than that of all of the neighboring nodes in the skeletal graph.
That is: we mark the local maxima, i.e. the mountain tops of the UoC as being central.
We also mark whole bones as being central if they are significant according to a common significance measure.

\subsubsection{Significance measure}\label{sec:significance_measure}
Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the angle $\angle{p_ovp_1}$ between a location $v$ on a bone of the skeleton and its two supporting polygon points $p_0$ and $p_1$.\cite{attali1996modeling}
Bones are significant if the bisector angle exceeds $\alpha_\text{max}$ which is governed by the beading strategy.

@@

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/naive_overfill_underfill.pdf}
\caption{
Overfill and underfill areas in a naive beading using a constant bead width $w$ of a wedge area with vertex angle $\beta$.
The underfill areas (light blue) are mirrored versions of the overfill areas (dark red).
The bisector angle $a = 180\degree - \beta$ is the angle between a location $v$ and its support $p_0$ and $p_1$.
}
\label{naive_overfill_underfill}
\end{figure}

A computationally efficient way to compute whether an edge is significant can be obtained by looking at the ratio between feature radius $R$ and the Euclidean distance:
if $ | R(v_1) - R(v_0) | / |v_1 - v_0| >  \cos(\alpha_\text{max} / 2)$ then $\alpha > \alpha_\text{max}$.
See \cref{distance_based_angles}.
This means we can prevent executing trigonometric functions on \emph{each} of the bones in the skeleton.
Moreover the ratio has a clear geometrical interpretation as the slope of the ridge in the UoC surface.

This ratio can readily be applied to simple skeleton segments to determine whether they are significant.
For skeletal segments generated by a polygon vertex at $(0,d)$ and a line segment through $(0,0)$ and $(0,\epsilon)$ or another vertex $(0,0)$, we can determine the significant portion by evaluating $\frac{\partial R}{\partial x} > \cos(\alpha_\text{max} / 2)$.
For parabolas we introduce extra points in the discretization at the two bounds where $| x | = d  / \tan(\alpha_\text{max} / 2)$
and for bones with vertex-vertex support we introduce discretization points at the two bounds where $| x | = \nicefrac12 d  / \tan(\alpha_\text{max} / 2)$.
This ensures that the discretization doesn't alter the extent and existence of marked central regions.
See \cref{discretization}.

@@

\subsubsection{Marking filtering}
Using the significance measure and the local maximum feature radius condition we initialize all marked bones and nodes.
We then filter out high frequency changes in the marking in order to ensure that the output of our technique is smooth. 
We perform filtering on the unmarked regions, because unmarking central regions could reintroduce large over- and underfill areas.
From each marked node $v_0$ with an upward unmarked bone attached we walk along the upward edges;
if the total length traversed until we reach another marked node $v_1$ is shorter than some filter distance $d_\text{max}^\text{unmarked}$, we mark all bones encountered as being central.
